---
title: "Report for Penguin `r params$id`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
format: html
params:
  id: "id"
---

```{r}
#| echo: false
knitr::opts_chunk$set(
  echo = FALSE
)
```


```{r}
#| eval: false

# grabs the whole df, mostly for a check
df |> knitr::kable()
```

```{r}
#| eval: false

# filter when df$id is in params$id
dplyr::filter(df, id %in% params$id) |>  
  knitr::kable()
```

## Penguin Report

Penguin number `r params$id` is a `r df$sex[df$id %in% params$id]` of the `r df$species[df$id %in% params$id]` species and was recorded on the island of `r df$island[df$id %in% params$id]` in `r df$year[df$id %in% params$id]`. This penguin has a body mass of `r df$body_mass_g[df$id %in% params$id]`(g), bill length of `r df$bill_length_mm[df$id %in% params$id]`(mm), and bill depth of `r df$bill_depth_mm[df$id %in% params$id]`(mm).

|                                                          |                                                        |                                                                |
|-----------------------|----------------------|---------------------------|
| ID: `r df$id[df$id %in% params$id]`                      | Species: `r df$species[df$id %in% params$id]`          | Sex: `r df$sex[df$id %in% params$id]`                          |
| Year: `r df$year[df$id %in% params$id]`                  | Island: `r df$island[df$id %in% params$id]`            | Body Mass: `r df$body_mass_g[df$id %in% params$id]`            |
| Bill Length: `r df$bill_length_mm[df$id %in% params$id]` | Bill Depth: `r df$bill_depth_mm[df$id %in% params$id]` | Flipper Length: `r df$flipper_length_mm[df$id %in% params$id]` |

```{r}
library(ggplot2)
library(gghighlight)
```


```{r}
#| label: fig-plot
#| fig-cap: "Plot"
#| warning: false
#| message: false
ggplot(data = df,
                aes(x = flipper_length_mm,
                    y = bill_length_mm)) +
  geom_point(aes(color = species,
                 shape = species),
             size = 3,
             alpha = 0.8) +
  gghighlight(df$id %in% params$id,
              label_key = id)
```
